### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
Figures - updating capitions. got to Decon Films.

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Bulk.png}
	\caption[Table of contents Capition]{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
	\label{fig:DSC_vHeatingRate_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Film.png}
	\caption[Table of contents Capition]{Unrelaxed film \MgZnCa~ heated at various heating rates. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
	\label{fig:DSC_vHeatingRate_Film}
\end{figure}

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
	\caption[Table of contents Capition]{Fitted \acrfull{m} for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
	\label{fig:Fragility_BulkFilm_mValue}
\end{figure}

@@

%MultiFigure
\begin{figure}[b]
	\centering
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_5Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_10Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_15Ks_result_A5lsc.png}
	\medskip
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_20Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_30Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_40Ks_result_A5lsc.png}
	\medskip
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_60Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_80Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_100Ks_result_A5lsc.png}
	\caption{\acrshort{dsc} deconvolution for the bulk. From left to right, top to bottom, 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
	\label{fig:DSC_Bulk_Decon}
\end{figure}

%MultiFigure
\begin{figure}[b]
	\centering
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_15Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_20Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_30Ks_result_A5lsc.png}
	\medskip
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_40Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_60Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_80Ks_result_A5lsc.png}
	\medskip
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_100Ks_result_A5lsc.png}
	\caption{\acrshort{dsc} deconvolution for the film. From left to right, top to bottom, 15, 20, 30, 40, 60, 80, 100 K/min.}
	\label{fig:DSC_Film_Decon}
\end{figure}

>>>>

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Bulk.png}
	\caption{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various \acrfullpl{ht}. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the $100 K/min$ sample.}%global caption
	\label{fig:DSC_vHeatingRate_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Film.png}
	\caption{Unrelaxed film \MgZnCa~ heated at various \acrfullpl{ht}. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the $100 K/min$ sample.}%global caption
	\label{fig:DSC_vHeatingRate_Film}
\end{figure}

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
	\caption{Fitted \acrfull{m} for the \MgZnCa~ system obtained from the \Tg~ of \acrshort{dsc} at various \acrfullpl{ht} for the bulk and film.}
	\label{fig:Fragility_BulkFilm_mValue}
\end{figure}

@@

%MultiFigure
\begin{figure}[b]
	\centering
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_5Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_10Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_15Ks_result_A5lsc.png}
	\medskip
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_20Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_30Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_40Ks_result_A5lsc.png}
	\medskip
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_60Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_80Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_100Ks_result_A5lsc.png}
	\caption{\acrshort{dsc} deconvolution for the bulk at various \glspl{ht}. From left to right, top to bottom, \gls{ht} = 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
	\label{fig:DSC_Bulk_Decon}
\end{figure}

%MultiFigure
\begin{figure}[b]
	\centering
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_15Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_20Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_30Ks_result_A5lsc.png}
	\medskip
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_40Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_60Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_80Ks_result_A5lsc.png}
	\medskip
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_100Ks_result_A5lsc.png}
	\caption{\acrshort{dsc} deconvolution for the film at various \glspl{ht}. From left to right, top to bottom, \gls{ht} = 15, 20, 30, 40, 60, 80, 100 K/min.}
	\label{fig:DSC_Film_Decon}
\end{figure}
